Accreditation Thoughts

### 2019-09-11 JHDNotes.tex
Added Comments
Added some dates
Added CEP etc.

\font\manual=manfnt
\def\dbend{{\manual\char127}}
\def\eqq{{\buildrel?\over=}}
\def\C{\mathbf{ C}}
\def\N{\mathbf{ N}}
\def\Q{\mathbf{ Q}}
\def\R{\mathbf{ R}}
\def\Z{\mathbf{Z}}
\def\F{\mathbf{F}}
\def\softO{\tilde{\cal O}}
\def\O{{\cal O}}
%\def\N{{\bf N}}
%\def\Q{{\bf Q}}
%\def\R{{\bf R}}
%\def\Z{{\bf Z}}
\def\action#1{\hfil\rlap{\bf#1}\break}
\def\pcite#1{[#1]}
\def\Res{\mathop{\rm Res}\nolimits}
\def\r#1#2{``#1''$\rightarrow$``#2''}
\documentclass{article}
\bibliographystyle{alphaurl}
\usepackage[hyphens]{url}
%\usepackage{enumitem}
\usepackage{pdfpages}
\usepackage{verbatim}
\usepackage{hyperref}
\usepackage{combelow}
\usepackage[show]{ed}
\usepackage{graphicx}
\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{notation}{Notation}
\newtheorem{example}{Example}
\newtheorem{problem}{Problem}
\def\decision#1{\par{\bf #1}}
\pagestyle{empty}
\begin{document}
\author{Notes by J.H.Davenport}
\title{Accreditation Thoughts}
\date{11 September 2019}
\maketitle
Note \url{https://hbr.org/2019/08/every-computer-science-degree-should-require-a-course-in-cybersecurity}
\section{Possible Questions for Paul to ask Seoul 8+6}
\begin{itemize}
\item[0)]By CyberSecurity we include what might be called "Information Security, IT Security etc."
\item Is there any CyberSecurity in your professional requirements currently?
\item  Do you have plans to change this
\item Are there any specific detailed requirements
\item Is there any quantification of how much CyberSecurity there should be.
\item Any other comments
\end{itemize}

\section{}
\end{document}
\section{}
\begin{description}
\item[Q]
\item[A]
\item[Q]
\item[A]
\end{description}

>>>>

\font\manual=manfnt
\def\dbend{{\manual\char127}}
\def\eqq{{\buildrel?\over=}}
\def\C{\mathbf{ C}}
\def\N{\mathbf{ N}}
\def\Q{\mathbf{ Q}}
\def\R{\mathbf{ R}}
\def\Z{\mathbf{Z}}
\def\F{\mathbf{F}}
\def\softO{\tilde{\cal O}}
\def\O{{\cal O}}
%\def\N{{\bf N}}
%\def\Q{{\bf Q}}
%\def\R{{\bf R}}
%\def\Z{{\bf Z}}
\def\action#1{\hfil\rlap{\bf#1}\break}
\def\pcite#1{[#1]}
\def\Res{\mathop{\rm Res}\nolimits}
\def\r#1#2{``#1''$\rightarrow$``#2''}
\documentclass{article}
\bibliographystyle{alphaurl}
\usepackage[hyphens]{url}
%\usepackage{enumitem}
\usepackage{pdfpages}
\usepackage{verbatim}
\usepackage{hyperref}
\usepackage{combelow}
\usepackage[show]{ed}
\usepackage{graphicx}
\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{notation}{Notation}
\newtheorem{example}{Example}
\newtheorem{problem}{Problem}
\def\decision#1{\par{\bf #1}}
\pagestyle{empty}
\begin{document}
\author{Notes by J.H.Davenport}
\title{Accreditation Thoughts}
\date{11 September 2019}
\maketitle
Note \url{https://hbr.org/2019/08/every-computer-science-degree-should-require-a-course-in-cybersecurity}
\section{Possible Questions for Paul to ask Seoul 8+6}
\begin{enumerate}
\item[0.]By CyberSecurity we include what might be called ``Information Security, IT Security etc.''
\item Is there any CyberSecurity in your professional requirements currently?
\item  Do you have plans to change this??
\item Are there any specific detailed requirements
\item Is there any quantification of how much CyberSecurity there should be?
\item Any other comments.
\end{enumerate}

\section{Publishing Venues}
\begin{description}
\item[IT Now]Being pursued, let by TomP.
\item[CEP]A UK focused conference (not necessarily a bad thing).
\item[\qquad11 October 2019]Deadline for abstracts
\item[\qquad18 October 2019]Deadline for full papers
\item[SIGCSE 2020]Main papers are closed, but there may be posters.
\item[ITiCSE]See \url{https://iticse.acm.org/ITiCSE2020/} --- apparently no dates.
\item[Koli]2019 closed 5 August. Presumbaly 2020 will be similar.
\item[Others]??
\end{description}
\end{document}
\section{}
\begin{description}
\item[Q]
\item[A]
\item[Q]
\item[A]
\end{description}
